---
title: "Comparing geoms"
format: html
editor: visual
---

# Setup

-   Load packages:

```{r}
#| label: load-packages

library(tidyverse)
library(openintro)
```

-   Prep data:

```{r}
#| label: mean-area-decade

duke_forest <- tucsonHousing %>%
  mutate(
    decade_built = (year_built %/% 10) * 10,
    decade_built_cat = case_when(
      decade_built <= 1950 ~ "1950 or before",
      decade_built >= 2000 ~ "2000 or after",
      TRUE ~ as.character(decade_built)
    )
  )

mean_area_decade <- tucsonHousing |>
  group_by(decade_built_cat) |>
  summarise(mean_area = mean(area))

mean_area_decade
```

# Histogram

Create a histogram of a continuous variable of your choice using geom_histogram(). Remember to set an appropriate binwidth. Describe the distribution that you see.

# Frequency polygon

Now create a frequency polygon of the same variable using geom_freqpoly(), but this time separate the data by a categorical variable. What differences do you notice when you compare groups?

# Scatter plot with smoothed line of best fit

Generate a scatterplot using geom_point() with two continuous variables from your dataset. Then use geom_smooth() to add a smoothed line of best fit to your scatterplot. How does this line help you understand the relationship between the two variables?

